lfl: Linguistic Fuzzy Logic in \R{} -- Part I

### 2021-02-06 article1.tex
Updates from Overleaf

If data frame is to be processed with the \code{lcut()} function, the result is created per column. Also note that the names of the resulting variables are derived from the column names of the input data frame:
%
\input{chunks/chunk-lcut.data.frame}
%
The given contexts, atomic expressions and hedges are recycled for each input numeric column. If a different setting is needed for each column, the arguments should be given as named lists as follows:
%
\input{chunks/chunk-lcut.data.frame2}

@@

The \code{fcut()} function works identically to \code{lcut()} for logical and factor input:
%
\input{chunks/chunk-fcut.logfact}
%
Numerical values are transformed with the \code{fcut()} function to triangular or raised-cosine membership degrees (depending on the \code{type} argument which has to be either \code{"triangle"} or \code{"raisedcos"}):
%
\input{chunks/chunk-fcut.numeric1}
%
The preceding example is identical to the call of the \code{triangular()} function:
%
\input{chunks/chunk-fcut.triangular}
%

>>>>

If data frame is to be processed with the \code{lcut()} function, the result is created per column. Also note that the names of the resulting variables are derived from the column names of the input data frame. For the sake of brevity, the result's column names are listed only:
%
\input{chunks/chunk-lcut.data.frame}
%
The given contexts, atomic expressions and hedges are recycled for each input numeric column. If a different setting is needed for each column, the arguments should be given as named lists as follows:
%
\input{chunks/chunk-lcut.data.frame2}

@@

The \code{fcut()} function works identically to \code{lcut()} for logical and factor input. However,
numerical values are transformed with the \code{fcut()} function to triangular or raised-cosine membership degrees (depending on the \code{type} argument which has to be either \code{"triangle"} or \code{"raisedcos"}):
%
\input{chunks/chunk-fcut.numeric1}
%
This is identical to the call of the \code{triangular()} function:
%
\input{chunks/chunk-fcut.triangular}
%
